\section{Experimental setup}\label{sec:experiments}
Although GCD can be applied to many tasks, we concentrate on three tasks in order to showcase its effectiveness: closed information extraction (cIE), entity disambiguation (ED), and constituency parsing (CP).
%
%We selected these two tasks as examples of complex grammar.
%One reason for their complexity is the large size of their vocabularies, which makes the grammar itself extensive and can potentially slow down the incremental parser.
%By demonstrating the feasibility of our approach in this challenging scenario, we can confidently assert that our method is practical for the majority of other structured outputs.
The first two tasks are examples where the output is restricted to a predefined set of entities and relations, while the third is an example of a task where the output is a complex tree structure.
All three tasks are challenging for LLMs in the few-shot setting, and we show that GCD can significantly improve LLM performance.



% one task by paragraph, the task name should be bold but without section number
\subsection{Closed information extraction (cIE)}
% Closed information extraction (cIE) is a task that involves extracting a comprehensive set of facts from natural language. Formally, given a knowledged base (KB) containing a collection of entities $\mathcal{E}$ and a collection of relations $\mathcal{R}$, the objective is to extract the complete set of fact triplets $y_\text{set}={(s, r, o) ,|, (s, r, o) \in \mathcal{E} \times \mathcal{R} \times \mathcal{E}}$ from a given textual input $x$. 
% After linearization of its output, done by \cite{josifoski-etal-2022-genie}, this structured output can be represented by a formal grammar, as illustrated in \Figref{fig:intro_figure}.
% This task is also known as \textit{joint entity and relation extraction}.
% The goal is to extract entities and relations from a given sentence and represent them in a structured format.
% The closed information extraction task distinguishes itself from the open information extraction task by requiring the output entity and relation to be from a predefined Knowledge Base(KB).

\xhdr{Task description} The goal of closed information extraction (cIE) is to extract a comprehensive set of facts from natural\hyp language text. Formally, given a knowledge base (KB) containing a collection of entities $\mathcal{E}$ and a collection of relations $\mathcal{R}$, the goal is to extract the complete set $y_\text{set} \subset \mathcal{E} \times \mathcal{R} \times \mathcal{E}$ of fact triplets from a given input text $x$.


\xhdr{Grammar}
We implement the grammar shown in \Figref{fig:intro_figure}.
Outputs are sets $y_\text{set}$ of triplets represented as structured sequences $y$ of tokens.
Each triplet consists of a subject entity name, a relation name, and an object entity name, each preceded by the special marker \texttt{[s]}, \texttt{[r]}, or \texttt{[o]}, respectively.
% The end of triplet is marked by \texttt{[e]}.
For instance, the two-triplet set
$y_\text{set}=\{$(Witchita, cast member, John Smith);
(Witchita, instance of, film)$\}$
is mapped to $y=$ ``\texttt{[s]} Witchita \texttt{[r]} cast member \texttt{[o]} John Smith \texttt{[s]} Witchita \texttt{[r]} instance of \texttt{[o]} film''.
Entity and relation names are restricted to a predefined set of entities (2.7M) and relations (888) from the Wikidata KB~\cite{wikidata}.
The grammar is context-free and allows an arbitrary number of triplets to be generated, including zero.

%Without explicitly mentioning, we report results on the FE linearization, as it yields better performance than SC.
%The given output linearization is consistent with the following formal grammar:
%\begin{align*}
%V &= \{S, T, A, B, C, E, R\},  \Sigma = \{\texttt{tokens}\} \\
%P& = \{S \rightarrow [S T | \epsilon], C \rightarrow [\texttt{[o]}\; E] \\
%&T \rightarrow [A B C \texttt{[e]}], E \rightarrow (\texttt{entity1} | \texttt{entity2} | ...), \\
%&A \rightarrow [\texttt{[s]}\; E], R \rightarrow (\texttt{rel1} | \texttt{rel2} | ...) \\
%&B \rightarrow [\texttt{[r]}\; R], \epsilon \rightarrow \texttt{</s>}\}
%\end{align*}
%\noindent In words, this translates to a grammar that starts with the empty string and allows for the addition of (i) a linearized triplet; or (ii) the end of sequence token \texttt{[e]} indicating the end of generation.
%%
%When producing a triplet, we are transitioning from the addition of the beginning of a subject token \texttt{[s]} followed by an entity from the entity catalog, to the beginning of a relation token \texttt{[r]} followed by a relation from the relation catalog, to the beginning of an object token \texttt{[o]} followed by an entity from the entity catalog and the end of triplet token \texttt{[e]}.
%In case of no triplet can be extracted from the input, the end of sequence token \texttt{</s>} is returned, marking the end of generation. An example is provided in \Figref{fig:parse_tree}


\xhdr{Dataset and evaluation metric}
We use the SynthIE-text dataset \cite{josifoski2023exploiting}, a synthetic dataset generated by prompting GPT-3.5.
This dataset, in comparison to previous ones like REBEL \cite{huguet-cabot-navigli-2021-rebel-relation}, is characterized by its larger size, increased diversity, and higher quality according to human ratings \cite{josifoski2023exploiting}.
The SynthIE-text dataset comprises 10K validation samples and 50K test samples.
For the purpose of evaluating our method in the few-shot scenario, we exclusively employ the test data.
We measure performance via triplet-based micro\hyp precision, recall, and F1-score, following \citet{josifoski-etal-2022-genie}.

% We use the SynthIE text dataset~\cite{josifoski2023exploiting}, which is a synthetic dataset generated from prompting the $text-davinci-003$.
% Compared with previous datasets, e.g., REBEL~\cite{huguet-cabot-navigli-2021-rebel-relation}, SynthIE is larger, more diverse and has a higher quality~\cite{josifoski2023exploiting}.
% SynthIE-text consists of 10K validation and 50K test samples.
% We do not make use of the validation data but only use the test data to evaluate the performance of our method in the few-shot setting.
% Due to computational constraints, we only use 1K samples from the test set for evaluation.
% %
% We measure the performance with triple based micro precision, recall and F1, the same evaluation metric as~\cite{josifoski2023exploiting}.




\subsection{Entity disambiguation (ED)}
% This task involves processing a text input that includes a mention of an entity, indicated by start and end  special tokens. The goal is to identify the most suitable entity identifier (name) from a predefined knowledge base, like Wikidata, that matches the mentioned entity. In certain cases, the input may also contain a set of candidate entities, marked by special tokens, to narrow the search scope. 

% This task is closely related to Entity Linking(EL).
% The input is a text containing a mention marked by a start and end position.
% The output is a entity name from a predefined knowledge base that best matches the mention.
% In some settings, the input may also contain a set of candidate entities which will narrow down the search space.

\xhdr{Task description} Entity disambiguation (ED) is the task of identifying the exact entity from a predefined knowledge base (\eg, Wikidata) referred to by a mention demarcated by special tokens in an input text.
In certain cases, the input may also contain a set of candidate entities to narrow the search scope.


\xhdr{Grammar}
We use grammar~2 of \Figref{fig:grammars_showcase_more}.
Following \citet{decao2021autoregressive}, the output structure consists of the mention followed by the inferred entity name in square brackets.
For instance, given the input ``There are two types of electricity: \texttt{<ent>} DC \texttt{</ent>} and AC'', the output is represented as ``There are two types of electricity: \texttt{<ent>} DC \texttt{[}Direct current\texttt{]} \texttt{</ent>} and AC''.
%
The grammar is regular and input-dependent.
It forces the model to generate the mention first, followed by an opening square bracket, an entity name from the candidate set, and finally a closing square bracket.
The candidate set is mention-dependent and is provided in the dataset.
%
To demonstrate the benefits of using an input-dependent grammar (IDG), we also experiment with an input-independent grammar (IIG).
For such a grammar, the candidate set needs to be the entire entity catalog of all entities (\eg, 470K in the data of \citet{le-titov-2018-improving}).
The constraints imposed by IIG are thus weaker than those of IDG.
Moreover, forcing the model via the IDG to repeat the left context (\eg, ``There are two types of electricity:'')\ may guide the model (via conditioning) in generating the correct entity name.
% For the above input, the output using an IIG is ``[Direct current]''.




\xhdr{Dataset and evaluation metric}
For the ED task, we employ six widely used datasets: AIDA-CoNLL~\cite{hoffart-etal-2011-robust}, MSNBC, ACE2004, AQUAINT, CLUEWEB, and WIKI~\cite{ClueWeb, ner_dataset}.
We use only the test data to evaluate the effectiveness of our method in a few-shot learning setting.
%
To measure the performance of our approach, we employ micro\hyp accuracy as the evaluation metric.
%
Further details about the datasets and evaluation metric are provided in Appendix~\ref{app_sec:entity_disambiguation}.

% \input{tables/ie_main_results.tex}

%\xhdr{Constraints}
%In this case, the constraints are only at the entity-level. We experiment with two different settings: (1) \color{red}input-independent grammar (static),\color{black} (2) input-dependent grammar (dynamic).
%The input-independent grammar encodes the entire entity universe, which is ). The input-dependent grammar encodes only the candidate entities provided along with the input(the the candidate set as from~\cite{decao2021autoregressive}). The number of input-dependent grammar files is equal to the number of data points, each of which is from 1KB to 30KB in size.
% We use constrained beam search with a beam size of 2 and a length penalty of 1.0.
% For this task, we use the top-1 generation for evaluation because the top generation is usually the correct entity.
% For other hyper-parameters, they are the same as the ones used in the cIE task.

% \input{tables/ed_main_results.tex}

\subsection{Constituency parsing (CP)}

\xhdr{Task description}
Constituency parsing (CP) is the task of parsing a sentence into a constituency parse tree capturing the syntactic structure of the sentence.

\xhdr{Grammar}
The output in CP must be a \textit{valid}---but not necessarily correct---constituency parse tree in Penn Treebank format \cite{evalb}.
A valid parse tree is defined as a tree that satisfies the constraints of
\textit{completeness} (every word in the sentence is included somewhere in the parse tree),
\textit{balanced brackets}
(every right bracket closes a previously unclosed left bracket, and every left bracket is eventually closed by a right bracket),
% (the number of left brackets should be equal to the number of right brackets),
and
\textit{label consistency} (the label of terminal and non-terminal nodes is consistent with the Penn Treebank format).

To capture these constraints, we use grammar~3 of \Figref{fig:grammars_showcase_more}.
% because the number of terminal nodes needs to be consistent with the number of words in the input sentence and each word needs to be included in the parse tree.
%
The grammar reproduces the input, represented as a sequence $x=\langle x_0, \dots, x_{n-1}\rangle$ of words, in left-to-right order, interspersing it with node labels and balanced brackets. In order to guarantee balanced brackets, the non-terminals $B_{i,j}$ count the number of opened left brackets \texttt{[} using the second subscript index $j$, and the rules ensure that the number of closed brackets can never exceed the number of previously opened brackets.
As an example, for the input $x=$ ``Nkurunziza leads Burundi from Gitega'', one valid parse tree would be $y=$ ``\texttt{[}S \texttt{[}NP Nkurunziza\texttt{]}\texttt{[}VP leads \texttt{[}NP Burundi\texttt{]}\texttt{[}PP from \texttt{[}NP Gitega\texttt{]}\texttt{]}\texttt{]}\texttt{]}''.

Note that the grammar in this task needs to be input-dependent
due to the aforementioned completeness constraint.
To demonstrate this, we also experiment with an input-independent grammar, a context-free grammar that recursively generates a parse tree of arbitrary size whose terminal nodes are anonymized as \texttt{XX}.
%
This grammar satisfies the balanced\hyp brackets and label\hyp consistency constraints, but not the completeness constraint.
As the grammar is context-free, it can generate a parse tree with an arbitrary number of nodes, possibly larger or smaller than the number of words in the input, which would result in an invalid parse tree.


\xhdr{Dataset and evaluation metric}
We use the test split of Penn Treebank to evaluate the effectiveness of our method in a few-shot learning setting.
Since we observed that the LLaMA models used in our experiments struggle to generate fully correct parse trees for long input sentences, both with and without constraints,
we use only sentences with gold parse trees shorter than 64 tokens.
%
We report the bracketing F1-score
% , recall, and precision
returned by the PYEVALB tool as our main evaluation metric.
%
As we observed that LLaMA without constraints often generates invalid parse trees,
% which PYEVALB tool reports as \textbf{state}=1.
we also report \textit{validity} (the percentage of valid parse trees)  as an additional metric.


\subsection{LLMs and prompting}\label{subsec:llm-prompting}

We utilize LLaMA~\cite{touvron2023llama} and Vicuna~\cite{vicuna2023} as backbone LMs, without performing any finetuning on downstream tasks.
Concretely, we evaluate the LLaMA-\{7B, 13B, 33B\} and Vicuna-\{7B, 13B\} models.
%
To construct the prompt, we begin by randomly selecting several data points from the training set and use them to manually craft multiple prompts for each task.
For more details about the used prompts and the decoding settings, see Appendices \ref{app_sec:prompt_construction} and \ref{appendix:decoding_settings}.


% We leave the combination of these techniques with our method as promising exploration directions.


% \input{sections/05_results.tex}

