
\section{Likelihood misalignment in GCD}

In the cIE and CP tasks, regardless of model size, the top generation is consistently an empty string (technically, a string ``\EOS''  consisting of the end-of-sequence token only) and the second most likely generation and subsequent generations are non-empty output sequences.
The issue is not unique to a particular LLM, but emerges consistently.
It is also similar to an observation by~\citet{stahlberg-byrne-2019-nmt}, who found that the most likely output of neural machine translation models is usually an empty string.

% \xhdr{Illustration}
We hypothesize that the empty\hyp string issue is caused by a likelihood misalignment between the grammar and the language model.
We use the cIE task as an example to illustrate the issue.
In the case of cIE, the first generated token must either be the left-bracket token ``\texttt{[}'' or the end-of-sequence token ``\EOS''.
The latter denotes the situation where no triplets can be extracted from the input.
With a beam size $k \geq 2$, both ``\texttt{[}'' and ``\EOS'' will be included in the beam at the first step.
Assume that the likelihood of ``\texttt{[}'' is $p$ and the likelihood of ``\EOS'' is~$q$.
Since ``\EOS'' denotes the end of the sequence, this generation is considered as a complete generation with a total likelihood of $q$.
In the other beam, the generation continues with ``\texttt{[}'' as the prefix, but as the generation proceeds, the likelihood of the generation may decrease below $q$.



% \xhdr{Hard constrains cause empty generation}
Since LLMs such as LLaMA are trained to maximize the likelihood of human language, the structure imposed by the grammar may be unnatural to the model, especially when the model is not finetuned on the respective task.
In the extreme case, the correct ground-truth output
% of the cIE task
could have a likelihood lower than that of the empty string ``\EOS'', resulting in the latter being returned as the top generation.
% As a result, the most likely generation found by beam search is always an empty string "\EOS" regardless of the model size.
This intuition gives rise to a simple fix: penalize the model for generating short strings, \eg, by adjusting the length normalization parameter $\alpha$ in the length-adjusted sentence score $S/m^{\alpha}$, where $S$ is the unadjusted score for the sentence and $m$ is the number of tokens in the sentence.
As shown in \Tabref{tab:LengthNormalizationMitigatesTheIssue}, this fix indeed solves the problem.

\input{tables/likelihood_misalignment}

% \xhdr{Instruction tuning alleviates the issue}
We also observed that the empty-string issue can be alleviated by using instruction\hyp tuned models.
%
While, without applying the aforementioned length normalization fix, LLaMA-13B always outputs the empty string ``\EOS'' as its top generation on the cIE task, the instruction\hyp tuned version (Vicuna-13B) outputs non-empty output as its top generation only 46\% of the time.
(The smaller Vicuna-7B, however, still always outputs ``\EOS'' as its top generation.)

%We believe that the issue does not affect the ranking of the generations within non-empty strings but only introduces an empty string as the top-1 generation because of its special truncated log-likelihood.
