\section{Additional Experimental Results}\label{app_sec:additional_experimental_results}
\subsection{Information Extraction}

\input{tables/sc_ie_results}
\input{tables/feR_ie_results}

\xhdr{Subject-Collapsed Linearization}
Subject-collapsed linearization is a variant of linearization where the subject is collapsed into the object.
It has the advantage of being more compact (token efficient) than the fully-expanded linearization, but it yields slightly lower performance, intuitively because it's less explicit.
Table~\ref{tab:subject-collapsed-linearization} shows that the constrained decoding approach brings a significant improvement over the unconstrained decoding approach for LMs of all sizes.
%
Compared with the results in Table~\ref{tab:subject-collapsed-linearization}, the performance of the subject-collapsed linearization is indeed lower than the fully-expanded linearization.

\xhdr{Adding all relations to the prompt}
With a maximum context length of 2048 tokens, it's not possible to add all the millions of \textbf{entities} to the prompt.
However, we can add all the \textbf{relations} to the prompt, which is a much smaller set (888 relations).
%
One may wonder if adding all the \textbf{relations} to the prompt would help the model to learn the relation extraction task better.
Because the model can copy the \textbf{relation} from the prompt and this may make the task easier.
However, we find that adding all the \textbf{relations} to the prompt does not help the model to learn the relation extraction task better.
Table~\ref{tab:InformationExtractionResults_Relations} shows that adding all the \textbf{relations} to the prompt only brings a small improvement over the baseline.



\xhdr{Constituency Parsing with Vicuna}
\input{tables/cp_vicuna}
We also evaluate the constrained decoding approach on the constituency parsing task with the instruction-tuned model Vicuna.
Table~\ref{tab:ConstituencyParsingResultsWithVicuna} shows Vicuna's performance is even worse than the LLaMA model.



